word lists

### 2021-04-20 analysis/word_lists.Rmd
add group size and base model

```{r}
md <- betal %>%
  select(-RatperWord, -aoa_german_b_sd)%>%
  full_join(setal%>%  select(german, english,word_freq,familiarity_m, aoa_german_s_m))%>%
  left_join(mor%>%select(english, aoa_mor, aoa_rating_english))%>%
  full_join(letal%>%left_join(clt))%>%
  filter(!is.na(german))%>%
  mutate(aoa_german_comb = ifelse(!is.na(aoa_german_b_m), aoa_german_b_m, 
                           ifelse(!is.na(aoa_german_s_m), aoa_german_s_m, aoa_german_l_m)))%>%
  select(german, word_freq, familiarity_m,aoa_german_b_m, aoa_german_s_m, aoa_german_l_m,aoa_german_comb,clt,english,aoa_mor,aoa_rating_english)%>%
  arrange(aoa_german_comb)%>%
  mutate(select = ifelse(clt == "yes", "x", ""), 
         word_freq = as.numeric(word_freq))%>%
  mutate_if(is.numeric, round, digits = 2)

write_xlsx(md, path = "../data/word_list.xlsx")

str(md)
```

>>>>

```{r}
md <- betal %>%
  select(-RatperWord, -aoa_german_b_sd)%>%
  full_join(setal%>%  select(german, english,word_freq,familiarity_m, aoa_german_s_m))%>%
  left_join(mor%>%select(english, aoa_mor, aoa_rating_english))%>%
  full_join(letal%>%left_join(clt))%>%
  filter(!is.na(german))%>%
  mutate(aoa_german_comb = ifelse(!is.na(aoa_german_b_m), aoa_german_b_m, 
                           ifelse(!is.na(aoa_german_s_m), aoa_german_s_m, aoa_german_l_m)))%>%
  select(german, word_freq,aoa_german_b_m, aoa_german_s_m, aoa_german_l_m,aoa_german_comb,clt,english,aoa_mor,aoa_rating_english)%>%
  arrange(aoa_german_comb)%>%
  mutate(select = ifelse(clt == "yes", "x", ""), 
         word_freq = as.numeric(word_freq))%>%
  mutate_if(is.numeric, round, digits = 2)
```

### Distribution of words by age

```{r}
md%>%
  ggplot(aes(x = aoa_german_comb))+
  geom_histogram(alpha = .5, fill = "firebrick",col = "black", position = "stack", binwidth = 0.25)+
  theme_minimal()+
  xlim(0,16)+
  scale_fill_viridis_d()
```
### Write Excel files for annotation

```{r}
md %>%
  filter(aoa_german_comb < 10)%>%
  mutate(group = as.numeric(factor(as.character(cut(row_number(), 10)))))%>%
  group_by(group)%>%
  group_walk(~write_xlsx(., paste0("../data/word_list_",.y$group,".xlsx")))

write_xlsx(md, path = "../data/word_list.xlsx")
```
